### 2017-02-03 local-capability-machine.tex
updated f1 to use fetch
Added new proof of f2s correctness using the scall lemma

              \subsection{Macro definitions}
              \begin{description}
              \item[\texttt{fetch} $r$ $f$] load the entry of the linking table corresponding to $f$ to register $r$.
              \item[\texttt{call} $r(\bar{r}_{\var{args}},\bar{r}_{\var{priv}})$] \forcenewline
                $\bar{r}_{\var{args}}$ and $\bar{r}_{\var{priv}}$ are lists of registers. An overview of this call:
                \begin{itemize}
                \item Set up activation record
                \item Create local enter capability for activation (protected return pointer)
                \item Clear unused registers
                \item Jump
                \item Upon return: Run activation code
                \end{itemize}
                A more detailed description of each of the above steps:
                \begin{description}
                \item [Set up activation record]\forcenewline
                  \begin{itemize}
                  \item Run malloc to get a piece of memory with space for:
                    \begin{itemize}
                    \item Words in $\bar{r}_{\var{priv}}$
                    \item Code return capability (opc)
                    \item Activation code
                    \end{itemize}
                  \item Store the words in $\bar{r}_{\var{priv}}$ to the activation record. 
                  \item Adjust a copy of the current pc to point to the return address in code and save it to the activation record.
                  \item Write the activation code to the activation record.
                  \end{itemize}
                \item [Create local enter capability for activation] Adjust the capability for the activation record to point to the beginning of the activation record and restrict it to a local enter-capability. Place this capability in $r_0$.
                \item [Clear unused registers]
                  Clear all the register that are not $\pcreg$, $r$, $r_0$ or in $\bar{r}_{\var{args}}$.
                \item [Jump] Jump to $r$
                \item [Activation code] The activation code does the following:
                  \begin{itemize}
                  \item Move the stored ``private'' words in to their respective $\bar{r}_{\var{priv}}$ registers.
                    % \item Clear all registers but $r_1$, $\pcreg$, and $\bar{r}_{\var{priv}}$.
                  \item Load the return capability to $\pcreg$
                  \end{itemize}
                \end{description}
              \item[\texttt{malloc $r$ $n$}] Calls malloc to allocates a piece of memory of size $n$. The capability will be stored in register $r$.

@@

              Assembly program not using stack. Assume that $\mathtt{r_l} \not\in \{\pcreg,r_0 \}$ is a register.
\begin{verbatim}
f1: malloc r_l 1
    store r_l 1
    call adv([],[r_l])
    assert r_l 1
1f: halt
\end{verbatim}

@@

          \item $\npair[n'-1]{c_\adv} \in \stdvr(W)$: for $n'' <
            n'-1$ and $W' \futurestr W$ show:
            \\$\npair[n'']{\updatePcPerm{c_\adv}} \in \stder(W')$.
            Use FTLR. \label{f1:adv}
          \end{enumproof}
        \end{enumproof}
      \item The last case follows from Lemma~\ref{lem:mem-sat-static}
      \end{enumproof}
    \end{enumproof}
  \item $\npair[n']{\reg_0\update{\pcreg}{\updatePcPerm{c_{\var{adv}}}}\update{r_1}{c_{\var{adv}}}\update{r_0}{c_{ar}'}} \in \stdrr(W)$
    \begin{enumproof}
    \item case: $\npair[n']{c_{\var{adv}}} \in \stdvr(W)$
      \begin{enumproof}
      \item Similar to \ref{f1:adv}
      \end{enumproof}
    \item case: $\npair[n']{c_{\var{ar}}'} \in \stdvr(W)$.
      \begin{enumproof}
      \item Let $n'' < n'$ and $W' \futurewk W$ be given and show $\npair[n'']{\updatePcPerm{c_{\var{ar}}'}} \in \stder(W')$\\
        Let $n^{(3)} \leq n''$, $\heapSat[\ms']{n^{(3)}}{W'}$, and $\npair[n^{(3)}]{\reg}$ be given\\
        Show: $\npair[n^{(3)}]{(\reg\update{\pcreg}{\updatePcPerm{c_{\var{ar}}'}},\ms')} \in \observations(W')$\\
        Assume $(\reg\update{\pcreg}{\updatePcPerm{c_{\var{ar}}'}},\ms' \uplus \ms_{\var{frame}}) \step[k''] (\halted, m')$, for some $k'' \leq n^{(3)}$, $m'$ and $\ms_{\var{frame}}$. Due to $\heapSat[\ms']{n^{(3)}}{W'}$, $\ms_{f1}$, $\ms_\flag$, $\ms_{\var{ar}}'$, and $\ms_l$ are unchanged. \\
        The execution loads $c_l$ to $r_l$ and jumps to $c_{f1}^{(3)}$ (the point just before the assertion). As $\ms_l = 1$, the assertion is successful and the execution halts. In other words, there were no changes to the memory.\\
        Use $W'$, $\ms_r = \emptyset$, and $\ms'$ to get the desired result, i.e., $m' = \ms' \uplus \ms_{\var{frame}}$ and $\heapSat[\ms']{n^{(3)}-k''}{W'}$ (using downwards closure of memory satisfaction).          
      \end{enumproof}
    \item case: $\npair[n']{0} \in \stdvr(W)$ (the contents remaining registers)\\
      Trivial to show.
    \end{enumproof}
  \end{enumproof}
  Get
  \[
    \npair[n']{(\reg_0\update{\pcreg}{\updatePcPerm{c_{\var{adv}}}}\update{r_1}{c_{\var{adv}}}\update{r_0}{c_{ar}'},m^{(3)})} \in \observations(W)
  \]
  By initial assumption of the lemma, the execution halts. Use $\ms_{\var{frame}}$, $m'$ and the number of steps it takes to halt to get:
  $W' \futurestr W$, $\ms_r$ and $\ms'$ s.t. $m' = \ms_r \uplus \ms' \uplus \ms_{\var{frame}}$ and $\heapSat[\ms']{n}{W'}$. As $\iota_\flag$ is a permanent region, we know it is still in $W'$, so $m'(\flag) = 0$.
\end{proof}

@@

\begin{lemma}[Correctness lemma for \texttt{f2}]
  \label{lem:correctness-f2}
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\olf) \\
    c_{f2} & \defeq ((\rwx,\glob),\mathtt{f2}-\olf,\mathtt{2f},\mathtt{f2}) \\
    c_\malloc & \defeq ((\entry,\glob),\start_\malloc,\addrend_\malloc,\start_\malloc+\olf) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_\stk,\start_\stk-1) \\
    \reg & \in \Regs \\
    m & \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_{\var{link}} \uplus 
        \hs_\adv \uplus 
        \ms_{\malloc} \uplus 
        \ms_{\var{stk}} \uplus
        \ms_{\var{frame}} 
  \end{align*}
  and
  \begin{itemize}
  \item $c_\malloc$ satisfies the specification for malloc.
  \end{itemize}
  where 
  \begin{align*}
    &\dom(\hs_{f2}) = [\mathtt{f2}-\olf,\mathtt{2f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link+1]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]} \qquad \text{ for all $n \in \nats$}
  \end{align*}
  and
  \begin{itemize}
  \item $\ms_{f2}(\mathtt{f2}-\olf) = ((\readonly,\glob),\link,\link+1,\link)$, $\ms_{f2}(\mathtt{f2}-\olf+1) = ((\readwrite,\glob),\flag,\flag,\flag)$, the rest of $\hs_{f2}$ contains the code of $f2$.
  \item $\ms_\flag = [\flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
  \item $\hs_\adv$ is only instructions and possibly a global read-only capability for $\hs_\link$
  \end{itemize}
  if 
  \[
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
  \]
  then
  \[
    m'(\flag) = 0
  \]  
\end{lemma}
\begin{proof}[Proof of lemma~\ref{lem:correctness-f2}]
  Let $n$ be given and make the assumptions of the lemma. Consider the execution until just after the jump to $\adv$, i.e.,
  \begin{multline*}
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[k] \\
    (\reg_0\update{\pcreg}{\updatePcPerm{c_\adv}}\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''},m'')
  \end{multline*}
  Where 
  \[
    m''  \defeq \hs_{f2} \uplus 
    \hs_\flag \uplus                
    \ms_\link \uplus 
    \hs_\adv \uplus 
    \ms_\malloc \uplus 
    \ms_\stk' \uplus
    \ms_{\var{frame}}
  \]
  Only the stack part of memory has changed. The stack and register-file at this point of execution is illustrated in figure~\ref{fig:f2-stack-before-adv}, where
  \begin{itemize}
  \item The range of authority for 
    \begin{itemize}
    \item $c_\stk'$ is $[\start_\stk,\addrend_\stk]$ (the entire stack)
    \item $c_\stk''$ is $[\start_\stk'',\addrend_\stk]$ (the unused part of the stack)
    \end{itemize}
    the two stack capabilities have the same permissions as $c_\stk$
  \item $c_{f2}'$ points to the return address in f2's code.
  \item $c_{\var{prp}}$ is a local enter-capability (with authority of all of the stack).
  \item Notice: $f2$ has no return capability, so $r_0$ was not listed as a private register in the call.
  \end{itemize}

@@

\begin{lemma}[$\mathtt{scall}$ works]
  \label{lem:scall-works}
  If
  \begin{itemize}
  \item $\memSat[n]{\ms}{\revokeTemp{W}}$ 
  \item $\dom(\ms_f) \cap (\dom(\ms_\stk \uplus \ms_{\mathit{unused}} \uplus \ms)) = \emptyset$
  \item $(\reg,\ms) \text{ is looking at }
    \mathtt{scall}\;r(\overline{r_{\mathit{arg}}},
    \overline{r_{\mathit{priv}}}) \text{ followed by } c_{\mathit{next}}$
  \item $\reg \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}$ unused}$
  \item[Hyp-Callee] If
    \begin{itemize}
    \item $\dom(\ms_{\mathit{unused}}) = \dom(\ms_{\mathit{act}}
      \uplus \ms_{\mathit{unused}}')$,
    \item $W' =
      \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk\uplus\ms_{\mathit{act}} \uplus \ms_f),\iota^{\pwl}(\dom(\ms_{\mathit{unused}}'))]$,
    \item $\memSat[n-1]{\ms''}{W'}$
    \item $\reg' \text{ points to stack with $\emptyset$ used and $\ms_{\mathit{unused}}'$ unused}$
    \item $\reg'= \reg_0[\pcreg\mapsto\updatePcPerm{\reg(r)},
      \overline{r_{\mathit{arg}}} \mapsto \reg(\overline{r_{\mathit{arg}}}),r_0
      \mapsto c_{\mathit{ret}}, r_\stk \mapsto \_, r \mapsto \reg(r)]$ 
    \item $\npair[n-1]{c_{\mathit{ret}}} \in \stdvr(W')$
    \item $\npair[n-1]{c_\stk} \in \stdvr(W')$
    \end{itemize}

    then we have that $(n-1,(\reg',\ms'')) \in \observations(W')$
  \item[Hyp-Cont] If
    \begin{itemize}
    \item $n' \leq n-2$
    \item $W'' \futurewk \revokeTemp{W}$
    \item $\memSat[n']{\ms''}{\revokeTemp{W''}}$ 
    \item for all $r$, we have that:
      \begin{equation*}
        \reg'(r)
        \begin{cases}
          = c_{\mathit{next}} &\text{ if } r = \pcreg\\
          = \reg(r)&\text{ if } r \in \overline{r_{\mathit{priv}}}\\
          \in \stdvr(\revokeTemp{W''}) &\text{ if $\reg'(r)$ is a global capability and } r \not\in \{\pcreg,\overline{r_{\mathit{priv}}}, r_\stk\}
        \end{cases}
      \end{equation*}
    \item $\reg' \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}''$ unused}$ for some $\ms_{\mathit{unused}}''$
    \end{itemize}

    then we have that $(n', (\reg',\ms'' \uplus \ms_f \uplus \ms_\stk \uplus \ms_{\var{unused}}'')) \in \observations(W'')$
  \end{itemize}
  Then 
  \begin{itemize}
    \item $\npair{(\reg,\ms \uplus \ms_f \uplus \ms_\stk \uplus \ms_{\var{unused}})} \in \observations(W)$
  \end{itemize}

>>>>

              \subsection{Macro definitions}
              \begin{description}
              \item[\texttt{fetch} $r$ $f$] load the entry of the linking table corresponding to $f$ to register $r$.
              \item[\texttt{call} $r(\bar{r}_{\var{args}},\bar{r}_{\var{priv}})$] \forcenewline
                $\bar{r}_{\var{args}}$ and $\bar{r}_{\var{priv}}$ are lists of registers. An overview of this call:
                \begin{itemize}
                \item Set up activation record
                \item Create local enter capability for activation (protected return pointer)
                \item Clear unused registers
                \item Jump
                \item Upon return: Run activation code
                \end{itemize}
                A more detailed description of each of the above steps:
                \begin{description}
                \item [Set up activation record]\forcenewline
                  \begin{itemize}
                  \item Run malloc to get a piece of memory with space for:
                    \begin{itemize}
                    \item Words in $\bar{r}_{\var{priv}}$
                    \item Code return capability (opc)
                    \item Activation code
                    \end{itemize}
                  \item Store the words in $\bar{r}_{\var{priv}}$ to the activation record. 
                  \item Adjust a copy of the current pc to point to the return address in code and save it to the activation record.
                  \item Write the activation code to the activation record.
                  \end{itemize}
                \item [Create local enter capability for activation] Adjust the capability for the activation record to point to the beginning of the activation record and restrict it to a local enter-capability. Place this capability in $r_0$.
                \item [Clear unused registers]
                  Clear all the register that are not $\pcreg$, $r$, $r_0$ or in $\bar{r}_{\var{args}}$.
                \item [Jump] Jump to register $r$
                \item [Activation code] The activation code does the following:
                  \begin{itemize}
                  \item Move the stored ``private'' words in to their respective $\bar{r}_{\var{priv}}$ registers.
                    % \item Clear all registers but $r_1$, $\pcreg$, and $\bar{r}_{\var{priv}}$.
                  \item Load the return capability to $\pcreg$
                  \end{itemize}
                \end{description}
              \item[\texttt{malloc $r$ $n$}] Calls malloc to allocates a piece of memory of size $n$. The capability will be stored in register $r$.

@@

              Assembly program not using stack. Assume that $\mathtt{r_l} \not\in \{\pcreg,r_0 \}$ is a register.
\begin{verbatim}
f1: malloc r_l 1
    store r_l 1
    fetch r_adv adv
    call r_adv([],[r_l])
    assert r_l 1
1f: halt
\end{verbatim}

@@

        \item $\npair[n'-1]{c_\adv} \in \stdvr(W)$: for $n'' <
          n'-1$ and $W' \futurestr W$ show:
          \\$\npair[n'']{\updatePcPerm{c_\adv}} \in \stder(W')$.
          Use FTLR. \label{f1:adv}
        \end{enumproof}

      \item The last case follows from Lemma~\ref{lem:mem-sat-static}
      \end{enumproof}
    \end{enumproof}
  \item $\npair[n']{\reg_0\update{\pcreg}{\updatePcPerm{c_{\var{adv}}}}\update{r_1}{c_{\var{adv}}}\update{r_0}{c_{ar}'}} \in \stdrr(W)$
    \begin{enumproof}
    \item case: $\npair[n']{c_{\var{adv}}} \in \stdvr(W)$
      \begin{enumproof}
      \item Similar to \ref{f1:adv}
      \end{enumproof}
    \item case: $\npair[n']{c_{\var{ar}}'} \in \stdvr(W)$.
      \begin{enumproof}
      \item Let $n'' < n'$ and $W' \futurewk W$ be given and show $\npair[n'']{\updatePcPerm{c_{\var{ar}}'}} \in \stder(W')$\\
        Let $n^{(3)} \leq n''$, $\heapSat[\ms']{n^{(3)}}{W'}$, and $\npair[n^{(3)}]{\reg}$ be given\\
        Show: $\npair[n^{(3)}]{(\reg\update{\pcreg}{\updatePcPerm{c_{\var{ar}}'}},\ms')} \in \observations(W')$\\
        Assume $(\reg\update{\pcreg}{\updatePcPerm{c_{\var{ar}}'}},\ms' \uplus \ms_{\var{frame}}) \step[k''] (\halted, m')$, for some $k'' \leq n^{(3)}$, $m'$ and $\ms_{\var{frame}}$. Due to $\heapSat[\ms']{n^{(3)}}{W'}$, $\ms_{f1}$, $\ms_\flag$, $\ms_{\var{ar}}'$, and $\ms_l$ are unchanged. \\
        The execution loads $c_l$ to $r_l$ and jumps to $c_{f1}^{(3)}$ (the point just before the assertion). As $\ms_l = 1$, the assertion is successful and the execution halts. In other words, there were no changes to the memory.\\
        Use $W'$, $\ms_r = \emptyset$, and $\ms'$ to get the desired result, i.e., $m' = \ms' \uplus \ms_{\var{frame}}$ and $\heapSat[\ms']{n^{(3)}-k''}{W'}$ (using downwards closure of memory satisfaction).          
      \end{enumproof}
    \item case: $\npair[n']{0} \in \stdvr(W)$ (the contents remaining registers)\\
      Trivial to show.
    \end{enumproof}
  \end{enumproof}
  Get
  \[
    \npair[n']{(\reg_0\update{\pcreg}{\updatePcPerm{c_{\var{adv}}}}\update{r_1}{c_{\var{adv}}}\update{r_0}{c_{ar}'},m^{(3)})} \in \observations(W)
  \]
  By initial assumption of the lemma, the execution halts. Use $\ms_{\var{frame}}$, $m'$ and the number of steps it takes to halt to get:
  $W' \futurestr W$, $\ms_r$ and $\ms'$ s.t. $m' = \ms_r \uplus \ms' \uplus \ms_{\var{frame}}$ and $\heapSat[\ms']{n}{W'}$. As $\iota_\flag$ is a permanent region, we know it is still in $W'$, so $m'(\flag) = 0$.
\end{proof}

@@

\begin{lemma}[Correctness lemma for \texttt{f2}]
  \label{lem:correctness-f2}
    c_{f2} & \defeq ((\rwx,\glob),\mathtt{f2}-\olf,\mathtt{2f},\mathtt{f2}) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_\stk,\start_\stk-1) \\
    c_\link & \defeq ((\readonly,\glob),\link,\link+1,\link)\\
    \reg & \in \Regs \\
    m & \defeq \hs_{f2} \uplus 
        \ms_{\var{stk}} \uplus
        \ms_{\var{frame}} 
    &\dom(\hs_{f2}) = [\mathtt{f2}-\olf,\mathtt{2f}] \\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]} \qquad \text{ for all $n \in \nats$}
  \item $\ms_{f2}(\mathtt{f2}-\olf) = ((\readonly,\glob),\link,\link+1,\link)$, $\ms_{f2}(\mathtt{f2}-\olf+1) = ((\readwrite,\glob),\flag,\flag,\flag)$, the rest of $\hs_{f2}$ contains the code of $f2$.
  \item $\hs_\adv(\start_\adv) = c_\link$ and $\forall \addr \in [\start_\adv+1,\addrend]\ldotp \ms_\adv(a) \in \ints$
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
\begin{proof}[Proof of Lemma~\ref{lem:correctness-f2} (using \texttt{scall} lemma)]
    Let $n$ be given and make the assumptions of the lemma. If we can show
      \label{pf:f2-sc:sfts-obs}
      \npair{(\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},\ms \uplus \ms_\stk)} \in \observations(W)
    for 
      \ms = \hs_{f2} \uplus 
            \ms_{\malloc} 
      W = [0 \mapsto \iota_{\malloc,0}]
          [1 \mapsto \iota^\sta (\perma, \ms_{f2} \uplus \ms_\flag)]
          [2 \mapsto \iota^{\sta,u} (\perma, \ms_\link)]
          [3 \mapsto \iota^{\nwl,p}_{\start_\adv,\addrend_\adv}]
    then we are done as we by assumption has
      (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m')
    so \ref{pf:f2-sc:sfts-obs} gives us a $W' \futurestr W$ where $W'$ satisfy part of $m'$. As $\ms_\flag$ is governed by a $\perma$ region, so it is unchanged. In other words
    So it suffices to show \ref{pf:f2-sc:sfts-obs}. To this end use Lemma~\ref{lem:anti-red-obs}. Let $\ms_f$ be given, then
  \begin{multline*}
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},\ms \uplus \ms_\stk \uplus \ms_f) \step[k] \\
    (\reg',\ms \uplus \ms_\stk' \uplus \ms_f)
  \end{multline*}
  \item \lookingat{(\reg',\ms)}{\scall{r_\adv}{}{r_l}}{c_{\var{next}}}
  \item $c_{\var{next}}$ is $c_{f2}$ that points to the instruction after the \texttt{scall}.
  \item \pointstostack{\reg'}{[\start_\stk \mapsto 1]}{\ms_\unused}
    \item for some $\ms_\unused$ where $\ms_\stk' = [\start_\stk \mapsto 1] \uplus \ms_\unused$.
  \item $\reg'(r_\adv) = c_\adv$
  In order to show the observation part necessary for Lemma~\ref{lem:anti-red-obs}, we use the "\texttt{scall} works"-Lemma (Lemma~\ref{lem:scall-works}). Show the following
  \item $\memSat{n-k}{\ms}{W}$\\
    Use Lemma~\ref{lem:disj-mem-sat} with
    \item $\memSat[n-k]{\ms_{f2} \uplus \ms_\flag}{[1 \mapsto \iota^\sta (\perma, \ms_{f2} \uplus \ms_\flag)]}$\\
      Lemma~\ref{lem:mem-sat-static}
      \item $\memSat[n-k]{\ms_\adv \uplus \ms_\malloc \uplus \ms_\link}{W_{\var{part}}}$ \\
          W_{\var{part}} = [0 \mapsto \iota_{\malloc,0}][2 \mapsto \iota^{\sta,u} (\perma, \ms_\link)][3 \mapsto \iota^{\nwl,p}_{\start_\adv,\addrend_\adv}]
        This amounts to
        \item $\npair[n-k-1]{\ms_\malloc} \in H \; 1 \; W_{\var{part}}$ where $H$ is the interpretaion of the $\iota_{\malloc,0}$ region.\\
          Follows from the malloc specification.
        \item $\npair[n-k-1]{\ms_\adv} \in H^\nwl \; 1 \; W_{\var{part}}$\\
          Can be shown using Lemma~\ref{lem:stau-subset-pwl}.
        \item $\npair[n-k-1]{\ms_\link} \in H^{\sta,u} (\ms_\link) \; 1 \; W_{\var{part}}$\\
            \item $\npair[n-k-2]{c_\malloc} \in \stdvr(W_{\var{part}})$
              Follows from Lemma~\ref{lem:malloc-in-vr}.
            \item $\npair[n-k-2]{c_\adv} \in \stdvr(W_{\var{part}})$\\
              Follows from Theorem~\ref{thm:ftlr} using Lemma~\ref{lem:nwlp-subset-pwl}.
    \item $\dom(\ms_{\mathit{unused}}) = \dom(\ms_{\mathit{act}} \uplus \ms_{\mathit{unused}}')$,
    \item $W' = \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk\uplus\ms_{\mathit{act}}),\iota^{\pwl}(\dom(\ms_{\mathit{unused}}'))]$,
    \item $\memSat[n-k-1]{\ms''}{W'}$
    \item $\reg' \text{ points to stack with $\emptyset$ used and $\ms_{\mathit{unused}}'$ unused}$
    \item $\reg'= \reg_0[\pcreg\mapsto\updatePcPerm{c_\adv},r_0 \mapsto c_{\mathit{ret}}, r_\stk \mapsto c_\stk, r_\adv \mapsto c_\adv]$ 
    \item $\npair[n-k-1]{c_{\mathit{ret}}} \in \stdvr(W')$
    \item $\npair[n-k-1]{c_\stk'} \in \stdvr(W')$
      (n-k-1,(\reg',\ms'')) \in \observations(W')
    By Theorem~\ref{thm:ftlr} we get
      \npair[n-k-1]{\updatePcPerm{c_\adv}} \in \stder(W')
    getting the desired result amounts to\footnote{We have memory satisfaction by assumption and the above entails the register-file is in the register-file relation.}
      \item $\npair[n-k-1]{c_\adv} \in \stdvr{W}$ \\
        To this end let $n' < n-k-1$ and $W'' \futurestr W'$ be given and show
          \npair[n']{\updatePcPerm{c_\adv}} \in \stder(W'')
        Follows from Theorem~\ref{thm:ftlr} and Lemma~\ref{lem:nwlp-subset-pwl}.
    \item $n' \leq n-2$
    \item $W'' \futurewk \revokeTemp{W}$
    \item $\reg''(\pcreg) = c_{\mathit{next}}$
    \item $\reg'' \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}''$ unused}$ for some $\ms_{\mathit{unused}}''$
      \npair[n']{(\reg'',\ms'' \uplus [\start_\stk \mapsto 1] \uplus \ms_{\var{unused}}'')} \in \observations(W'')
    From $\memSat[n']{\ms''}{\revokeTemp{W''}}$, we get that $\ms_{f2}$ is unchanged. Given a frame $\ms_f'$ and assuming $n'$ is sufficiently large, the execution continues as follows:
      (\reg'',\ms'' \uplus [\start_\stk \mapsto 1] \uplus \ms_{\var{unused}}'' \uplus \ms_f) \step[k] (\halted,\ms'' \uplus [\start_\stk \mapsto 1] \uplus \ms_{\var{unused}}'' \uplus \ms_f)
    because 1 is popped of the stack to a register, then it is compared with 1 in the assertion, so the assertion succeeds and halts immediately after.

    By assumption we had $\memSat[n']{\ms''}{\revokeTemp{W''}}$ which gives us exactly the memory satisfaction required by $\observations(W'')$.
  \end{enumproof}
\end{proof}

\begin{proof}[Proof of lemma~\ref{lem:correctness-f2}]
  Let $n$ be given and make the assumptions of the lemma. Consider the execution until just after the jump to $\adv$, i.e.,
  \begin{multline*}
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[k] \\
    (\reg_0\update{\pcreg}{\updatePcPerm{c_\adv}}\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''},m'')
  \end{multline*}
  Where 
  \[
    m''  \defeq \hs_{f2} \uplus 
    \hs_\flag \uplus                
    \ms_\link \uplus 
    \hs_\adv \uplus 
    \ms_\malloc \uplus 
    \ms_\stk' \uplus
    \ms_{\var{frame}}
  \]
  Only the stack part of memory has changed. The stack and register-file at this point of execution is illustrated in figure~\ref{fig:f2-stack-before-adv}, where
  \begin{itemize}
  \item The range of authority for 
    \begin{itemize}
    \item $c_\stk'$ is $[\start_\stk,\addrend_\stk]$ (the entire stack)
    \item $c_\stk''$ is $[\start_\stk'',\addrend_\stk]$ (the unused part of the stack)
    \end{itemize}
    the two stack capabilities have the same permissions as $c_\stk$
  \item $c_{f2}'$ points to the return address in f2's code.
  \item $c_{\var{prp}}$ is a local enter-capability (with authority of all of the stack).
  \item Notice: $f2$ has no return capability, so $r_0$ was not listed as a private register in the call.
  \end{itemize}

@@

\begin{lemma}[$\mathtt{scall}$ works]
  \label{lem:scall-works}
  If
  \begin{itemize}
  \item $\memSat[n]{\ms}{\revokeTemp{W}}$ 
  \item $\dom(\ms_f) \cap (\dom(\ms_\stk \uplus \ms_{\mathit{unused}} \uplus \ms)) = \emptyset$
  \item $(\reg,\ms) \text{ is looking at }
    \mathtt{scall}\;r(\overline{r_{\mathit{arg}}},
    \overline{r_{\mathit{priv}}}) \text{ followed by } c_{\mathit{next}}$
  \item $\reg \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}$ unused}$
  \item[Hyp-Callee] If
    \begin{itemize}
    \item $\dom(\ms_{\mathit{unused}}) = \dom(\ms_{\mathit{act}}
      \uplus \ms_{\mathit{unused}}')$,
    \item $W' =
      \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk\uplus\ms_{\mathit{act}} \uplus \ms_f),\iota^{\pwl}(\dom(\ms_{\mathit{unused}}'))]$,
    \item $\memSat[n-1]{\ms''}{W'}$
    \item $\reg' \text{ points to stack with $\emptyset$ used and $\ms_{\mathit{unused}}'$ unused}$
    \item $\reg'= \reg_0[\pcreg\mapsto\updatePcPerm{\reg(r)},
      \overline{r_{\mathit{arg}}} \mapsto \reg(\overline{r_{\mathit{arg}}}),r_0
      \mapsto c_{\mathit{ret}}, r_\stk \mapsto c_\stk, r \mapsto \reg(r)]$ 
    \item $\npair[n-1]{c_{\mathit{ret}}} \in \stdvr(W')$
    \item $\npair[n-1]{c_\stk} \in \stdvr(W')$
    \end{itemize}

    then we have that $\npair[n-1]{(\reg',\ms'')} \in \observations(W')$
  \item[Hyp-Cont] If
    \begin{itemize}
    \item $n' \leq n-2$
    \item $W'' \futurewk \revokeTemp{W}$
    \item $\memSat[n']{\ms''}{\revokeTemp{W''}}$ 
    \item for all $r$, we have that:
      \begin{equation*}
        \reg'(r)
        \begin{cases}
          = c_{\mathit{next}} &\text{ if } r = \pcreg\\
          = \reg(r)&\text{ if } r \in \overline{r_{\mathit{priv}}}\\
          \in \stdvr(\revokeTemp{W''}) &\text{ if $\reg'(r)$ is a global capability and } r \not\in \{\pcreg,\overline{r_{\mathit{priv}}}, r_\stk\}
        \end{cases}
      \end{equation*}
    \item $\reg' \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}''$ unused}$ for some $\ms_{\mathit{unused}}''$
    \end{itemize}

    then we have that $\npair[n']{(\reg',\ms'' \uplus \ms_f \uplus \ms_\stk \uplus \ms_{\var{unused}}'')} \in \observations(W'')$
  \end{itemize}
  Then 
  \begin{itemize}
    \item $\npair{(\reg,\ms \uplus \ms_f \uplus \ms_\stk \uplus \ms_{\var{unused}})} \in \observations(W)$
  \end{itemize}
